Bayes network classifiers for fMRI

### 2012-10-16 article/article.tex
article update

%% Abstract section.
\abstract{
Functional magnetic resonance imaging (fMRI) is a brain mapping technique that allows researchers to measure activity in a subject's brain. This technique is typically used to determine which areas of the brain are involved in performing a certain task. Using this knowledge, we may also be able to determine what task was performed by looking at fMRI data. In this paper, we will discuss the use of machine learning algorithms for the classification of fMRI data. By using classifiers we will try to predict the cognitive state of a subject, based on its brain activity during that time.
} % end of abstract

@@

%% The ``\maketitle'' command must be the first command after the
%% ``\begin{document}'' command. It prepares and prints the title block.
%% the only exception to this rule is the \firstsection command
\firstsection{Introduction}
\label{sec:introduction}
\maketitle
%% Now the actual contents of first section
Traditionally, it has been a challenge to relate between a simple cognitive state (such as `looking at a triangle`) and the corresponding activity of the brain \cite{Pone0001394}. This correspondence may even vary from subject to subject, making the challenge even bigger. Since the introduction of fMRI scans, researchers have been able to acquire detailed measurements of brain activity, allowing for machine learning methods to be applied for the detection of patterns in fMRI data.

@@

In total, we have data available for approximately 4000 voxels per scan, 54 scans per trial, 40 trials per subject, 6 subjects.

>>>>

%% Abstract section.
\abstract{
Functional magnetic resonance imaging (fMRI) is a brain mapping technique that allows researchers to measure activity in a subject's brain. This technique is typically used to determine which areas of the brain are involved in performing a certain task. Using this knowledge, we may also be able to determine what task was performed by looking at fMRI data. In this paper, we will discuss the use of machine learning algorithms for the classification of fMRI data. By using classifiers we will try to predict the cognitive state of subjects, based on their brain activity during that time.
} % end of abstract

@@

%% The ``\maketitle'' command must be the first command after the
%% ``\begin{document}'' command. It prepares and prints the title block.
%% the only exception to this rule is the \firstsection command
\firstsection{Introduction}
\label{sec:introduction}
\maketitle
%% Now the actual contents of first section
Traditionally, it has been a challenge to relate between a simple cognitive state (such as `looking at a triangle`) and the corresponding activity of the brain \cite{Pone0001394}. This correspondence may even vary from subject to subject, making the challenge even harder. Since the introduction of fMRI, researchers have been able to acquire detailed measurements of brain activity, allowing for machine learning methods to be applied for the detection of patterns in fMRI data.

@@

In total, we have data available for approximately 4800 voxels per scan, 54 scans per trial, 40 trials per subject, 6 subjects.
